CO($J$ = 3 $\rightarrow$ 2) observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with continuum detection in the foreground lensing FR-II radio galaxy at $z$ = 0.685

### 2015-06-23 skeleton.tex
Moving on to Analysis section

Observations of the CO($J$ = 3 $\rightarrow$ 2) rotation line ($\nu_{rest}$ = 345.7959899 GHz),
redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
J0939+8315 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I.: D. Riechers).
We used the 3mm receivers with a bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s$^{-1}$)
resolution to cover the CO($J$ = 3 $\rightarrow$ 2) line and the underlying 2.877 mm continuum emission. The CO($J$ = 3 
$\rightarrow$ 2) line was placed on the
upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The MIRIAD package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting, this yields a synthesized (clean) beam size of 13$\farcs$57 $\times$ 
5\farcs77 . The final rms noise is $\sigma$ = 0.7 Jy $\rm beam^{-1}$ over
a channel width of 135.4 MHz (corresponding to $\sim$378.1 km s$^{-1}$). The continuum image is created by
averaging over all the line-free channels, this yields a synthesized (clean) beam size of 16\farcs67 $\times$ 7\farcs17 and a 
rms noise of 0.55 mJy beam$^{-1}$.

% mom0 map channels [72, 85], each channel is 29.088 km/s, i.e. total velocity range is 378.144 km/s, which is 135.408 
MHz
\section{Results}\label{sec:res}
\subsection{New results: Continuum Emission}

%%Continuum: 104.2106 GHz (2.876794 mm observed frame)
% So integrated - peak should be approx. the extended components ~ (7.18 +/- 0.69 mJy - 5.56 +/- 0.54 mJy)
% max peak = 0.005347 \pm 5.0e-4
% VLA sigma = 6.41094e-05 Jy

%Deconvolution size bigger than expected (= just radio core):
%1) phase error that wasn't well calibrated (~30/360 $\times$\appox 16") ~ 1-2"
%2) low SNR giving rise to fitting error ~ 4" from `imfit`
%3) PA beam align with RG (radio galaxy) orientation
Averaging over all the line-free channels, we detect the continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 
mJy at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, hence we expect the continuum to be dominated by the foreground galaxy. The 
deconvolved source size of the continuum image is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60. At this 
frequency, we expect the emission from the radio core to dominate our continuum detection; however, the integrated flux 
density is measured to be 7.18 $\pm$ 0.69 mJy. Considering the fact that the orientation of the synthesized beam aligns with 
the axis along the lobes of the foreground radio galaxy as shown in Figure \ref{fig:cont}, we interpret this difference between 
the peak flux density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the 
continuum detection includes non-thermal emission from the lobes.
\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel}
\caption{The central cross indicates the position of the radio core of 3C220.3. Contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ of $\sigma$ = 0.0641 mJy beam$^{-1}$ and increment at steps of $\pm$2$^n\sigma$, 
where n is positive integers; contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam$^{-1}$.
Left:Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs67 $\times$ 7\farcs17, at P.A. = 
-58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid the 9 GHz emission (green) \citep{Haas14}. The rms in the 9GHz image is $\sigma$ 
= 0.0641 mJy beam$^{-1}$. The synthesized beam size of the VLA observations is 0$\farcs$60 $\times$ 0$\farcs$23 at P.A. 
76$\degr$. 
\label{fig:cont}}
\end{figure*}

\subsection{New results: CO($J$ = 3 $\rightarrow$ 2) line emission}
%peak 19.907623291015625 2.2045940408007811
%We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward SMM J0939+8315 at peak flux
%of blah sigma  of $ \sigma$ = blah mJy beam$^{-1}$.
We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background SMG SMM J0939+8315. We extract 
the spectrum and fit a single-component Gaussian as shown in Figure \ref{fig:mom0}, yielding peak flux density of 19.90 $\pm
$ 2.20 mJy, superimposed on a continuum level of 3.46 mJy, the FWHM of the Gaussian fit is 541.65 $\pm$ 31.91 km s
$^{-1}$. The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, where the 
synthesized beam size of the SMA observation is 1\farcs42$\times$1\farcs16, at P.A. -34.0\degr. Since the angular resolution 
of our CO measurement is 13$\farcs$57 $\times$ 5\farcs77 , the CO($J$ = 3 $\rightarrow$ 2) detection in the SMG is 
therefore spatially unresolved. We construct the velocity-integrated (moment-0) map of the CO($J$ = 3 $\rightarrow$ 2) 
emission using the uv-continuum subtracted data, the velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line flux is 14.6 $\pm$ 
0.9 Jy km s$^{-1}$.

Channel width used for mom0 map. and to get the integrated flux.

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel}
\includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$3$\sigma$, 
incrementing at
steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in 
the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$. The angular resolution is 13$\farcs$57 $\times$ 
5\farcs77, the beam size is shown in the bottom left corner. 
Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (green) with $
\sigma$ = 0.84 mJy beam$^{-1}$. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34\degr, as shown 
in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam 
size of the CARMA observations, hence the CO($J$ = 3 $\rightarrow$ 2) line detection is spatially unresolved.
%Bottom: The Gaussian-fitted line peak of CO($J$ = 3 $\rightarrow$ 2) is 23.36 $\pm$ 2.21 mJy (before continuum
%subtraction), and the integrated line flux over linewidth of $\sim$1000 km/s is 14.6 $\pm$ 0.9 Jy km s$^{-1}$
%(after continuum subtraction).  
Bottom: Solid black line shows our Gaussian fit to the CO ($J$ = 3 $\rightarrow$ 2) line profile. Yellow histogram shows the 
flux density as a function of velocity offset, where 0 km/s corresponds to $z$ = 2.2214. 
\label{fig:mom0}}
\end{figure*}

@@

>>>>

Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational transition ($\nu_{rest}$ = 345.7959899 GHz),
redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
J0939+8315 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I.: D. Riechers).
We used the 3mm receivers with a bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s$^{-1}$)
resolution to cover the CO($J$ = 3 $\rightarrow$ 2) line and the underlying 2.877 mm continuum emission. The CO($J$ = 3 
$\rightarrow$ 2) line was placed on the
upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The MIRIAD package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting, this yields a synthesized (clean) beam size of 13$\farcs$57 $\times$ 
5\farcs77 . The final rms noise is $\sigma$ = 0.7 Jy $\rm beam^{-1}$ over
a channel width of 135.4 MHz (corresponding to $\sim$378.1 km s$^{-1}$). The continuum image is created by
averaging over all the line-free channels, this yields a synthesized (clean) beam size of 16\farcs67 $\times$ 7\farcs17 and a 
rms noise of 0.55 mJy beam$^{-1}$.

% mom0 map channels [72, 85], each channel is 29.088 km/s, i.e. total velocity range is 378.144 km/s, which is 135.408 
MHz
\section{Results}\label{sec:res}
\subsection{New results: Continuum Emission} 
% So integrated - peak should be approx. the extended components ~ (7.18 - 5.56 mJy)
%      --- Integrated:   7.18 +/- 0.69 mJy
%      --- Peak:         5.56 +/- 0.54 mJy/beam

%Deconvolution size bigger than expected (if just radio core):
%1) phase error that wasn't well calibrated (~30/360 $\times$\appox 16") ~ 1-2"
%2) low SNR giving rise to fitting error ~ 4" from `imfit`
%3) PA beam align with RG (radio galaxy) orientation
Averaging over all the line-free channels, we detect the continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 
mJy beam$^{-1}$ at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame, corresponding to $\sim$2.79 mm at $z$ = 0.658. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, hence we expect the continuum to be dominated by the foreground galaxy. The 
deconvolved source size in the continuum image is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy. 
In Figure \ref{fig:cont}, we show the new measurement of the continuum emission at 104 GHz overlaid on the VLA 9 GHz continuum measurement reported by \citet{Haas14}. The figure demonstrates that at the resolution of our observation, the continuum detection is marginally resolved, it is therefore plausible that both non-thermal and thermal emissions from the lobes and the radio core contribute to the integrated flux density this frequency.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel}
\caption{The central cross indicates the position of the radio core of 3C220.3. Contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ of $\sigma$ = 0.0641 mJy beam$^{-1}$ and increment at steps of $\pm$2$^n\sigma$, 
where n is positive integers; contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam$^{-1}$.
Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs67 $\times$ 7\farcs17, at P.A. = 
-58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid the 9 GHz emission (green) \citep{Haas14}. The rms in the 9GHz image is $\sigma$ 
= 0.0641 mJy beam$^{-1}$. The synthesized beam size of the VLA observations is 0$\farcs$60 $\times$ 0$\farcs$23 at P.A. 
76$\degr$. 
\label{fig:cont}}
\end{figure*}

\subsection{New results: CO($J$ = 3 $\rightarrow$ 2) line emission}
We detect CO($J$ = 3 $\rightarrow$ 2) line emission toward the background SMG SMM J0939. We fit a four-parameter single-component Gaussian to the spectrum as shown in Figure \ref{fig:mom0}, yielding peak flux density of 19.9 $\pm
$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy at the peak position of the CO emission; and FWHM of 541.65 $\pm$ 31.91 km s$^{-1}$. 
The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, the 
synthesized beam size of the SMA observation is 1\farcs42$ \times $1\farcs16, at P.A. -34.0\degr. As such, the CO($J$ = 3 $\rightarrow$ 2) detection in the SMG is spatially unresolved. We construct a velocity-integrated (0th moment) map of the CO($J$ = 3 $\rightarrow$ 2) 
emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line flux of $S$ 14.6 $\pm$ 0.9 Jy km s$^{-1}$ over a velocity range of $\Delta$v = $\sim$378.1 km s$^{-1}$.

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel}
\includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$3$\sigma$, 
incrementing at
steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in 
the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$. The angular resolution is 13$\farcs$57 $\times$ 
5\farcs77, as shown in the bottom left corner. 
Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (green) with $
\sigma$ = 0.84 mJy beam$^{-1}$. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34\degr, as shown 
in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam 
size of the CARMA observations, hence the CO($J$ = 3 $\rightarrow$ 2) line detection is spatially unresolved. Bottom: Solid black line shows the Gaussian fit to the CO ($J$ = 3 $\rightarrow$ 2) line profile. Yellow histogram shows the 
flux density as a function of velocity offset, where 0 km/s corresponds to $z$ = 2.221. 
\label{fig:mom0}}
\end{figure*}

@@

Considering the fact that the orientation of the synthesized beam aligns with 
the axis along the lobes of the foreground radio galaxy as shown in Figure \ref{fig:cont}, we interpret this difference between 
the peak flux density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the 
continuum detection includes non-thermal emission from the lobes.
